Bricking up backdoors in Intrusion Detection Systems

### 2019-09-12 paper/paper.tex
Small changes

We make all our code publicly available at \todo{Insert link to GitHub repo}.

@@

In addition to fine-tuning we also tried fine-pruning~\cite{liu_fine-pruning:_2018}, preceding fine-tuning with a large number of different pruning strategies. From these experiments, only pruning a certain fraction of the \gls{mlp}'s first layer resulted in a discernible drop of backdoor efficacy after one epoch of fine-tuning, primarily for \cic{}.

@@

\section*{Acknowledgement}
The Titan Xp used for this research was donated by the NVIDIA Corporation. We thank Prof.~Andreas Rauber for his suggestions to improve the explainability plots.

>>>>

We make all our code publicly available at \url{https://github.com/CN-TU/ids-backdoor}.

@@

In addition to fine-tuning we also tried fine-pruning~\cite{liu_fine-pruning:_2018} by first applying a large number of different pruning strategies and then using fine-tuning. From all pruning strategies, only pruning a certain fraction of only the \gls{mlp}'s first layer resulted in a discernible drop of backdoor efficacy after one epoch of fine-tuning, primarily for \cic{}.

@@

\section*{Acknowledgements}
The Titan Xp used for this research was donated by the NVIDIA Corporation. We thank Prof.~Andreas Rauber for his suggestions to improve the explainability plots.
